cardinalR: Generating interesting high-dimensional data structures

### 2025-09-16 paper-cardinalR.Rmd
Added details regarding to the spread

The `gen_longlinear(n, p)` function simulates a high-dimensional linear structure with a dominant linear trend and small additive noise (`r knitr::asis_output(if (knitr::is_html_output()) { "Figure \\@ref(fig:linear)"} else { "Figure \\@ref(fig:linear-proj)"})`). Each variable $X_i$ is created as $X_i = \text{scale}_i \left(0, 1, \dots, n{-}1 + \epsilon\right) + \text{shift}_i$, where $\text{scale}_i \sim U(-10, 10)$ is randomly chosen direction and stretch, $\text{shift}_i \sim U(-300, 300)$ is large offset to spread features apart, and $\epsilon \sim N(0, 0.03n)$ is Gaussian noise.

@@

```{r trefoil-tb-pdf, eval=knitr::is_latex_output()}
trefoil_tb |> 
  kable(caption = "cardinalR trefoil data generation functions", format="latex", col.names = c("Function", "Explanation"), booktabs = T)  |>
  column_spec(1, width = "4cm") |>
  column_spec(2, width = "8cm")
```

>>>>

The `gen_longlinear(n, p)` function generates a high-dimensional dataset representing a long linear structure with noise. Each variable is formed as $X_i = \text{scale}_i \cdot (0,1,\dots,n{-}1 + \epsilon) + \text{shift}_i$, where $\text{scale}\_i \sim U(-10, 10)$ determines the orientation of the line in each dimension, $\text{shift}\_i \sim U(-300, 300)$ offsets the line to separate dimensions, and $\epsilon \sim N(0, (0.03n)^2)$ introduces Gaussian noise.

@@

```{r trefoil-tb-pdf, eval=knitr::is_latex_output()}

trefoil_tb |> 
  kable(caption = "cardinalR trefoil data generation functions", format="latex", col.names = c("Function", "Explanation"), booktabs = T)  |>
  column_spec(1, width = "4cm") |>
  column_spec(2, width = "8cm")
```

### 2025-09-16 paper-cardinalR.tex
Added details regarding to the spread

The \texttt{gen\_longlinear(n,\ p)} function simulates a high-dimensional linear structure with a dominant linear trend and small additive noise (Figure \ref{fig:linear-proj}). Each variable \(X_i\) is created as \(X_i = \text{scale}_i \left(0, 1, \dots, n{-}1 + \epsilon\right) + \text{shift}_i\), where \(\text{scale}_i \sim U(-10, 10)\) is randomly chosen direction and stretch, \(\text{shift}_i \sim U(-300, 300)\) is large offset to spread features apart, and \(\epsilon \sim N(0, 0.03n)\) is Gaussian noise.

>>>>

The \texttt{gen\_longlinear(n,\ p)} function generates a high-dimensional dataset representing a long linear structure with noise. Each variable is formed as \(X_i = \text{scale}_i \cdot (0,1,\dots,n{-}1 + \epsilon) + \text{shift}_i\), where \(\text{scale}\_i \sim U(-10, 10)\) determines the orientation of the line in each dimension, \(\text{shift}\_i \sim U(-300, 300)\) offsets the line to separate dimensions, and \(\epsilon \sim N(0, (0.03n)^2)\) introduces Gaussian noise.
